Supplementary Materials

### 2018-03-30 paper/appendix_modelDescription.tex
minor change in appendix

@@

\section{Appendix B: Code Example: Link Visualization with Model}
From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface. The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to supplied by the NLP model.

>>>>

\textbf{Comment} $\overleftarrow{\boldsymbol{a}}$ and $\overrightarrow{\boldsymbol{a}}$ are referred as \emph{att1} and \emph{att2} in the visualization.

@@

\section{Appendix B: Code Example: Link Visualization with Model}
From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface. The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.
